Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2020-01-26 manuscript/cover-letter/cover_letter.tex
Minor edit to cover letter

  Our findings answer several open questions in the field and point the way for future forecasting efforts.
  We find that genetic estimates of antigenic drift are insufficient replacements for the gold standard phenotypic measures provided by HI assays.
  We further show that the success of previous models based on these genetic estimates is due, in part, to inadvertantly borrowing information from the future.
  In contrast, we show that simple genetic estimates of functional constraint are superior to more detailed estimates provided by deep mutational scanning (DMS) measurements from a single background strain.
  The results suggest that future forecasting models should strive not to replace genetic fitness metrics with phenotypic metrics but to identify metrics that are the least likely to be affected by historical contingency.

>>>>

  Our findings answer several open questions in the field and point the way for future forecasting efforts.
  We find that genetic estimates of antigenic drift are insufficient replacements for the gold standard phenotypic measures provided by HI assays.
  We further show that the success of previous models based on these genetic estimates is due, in part, to inadvertantly borrowing information from the future.
  In contrast, we show that simple genetic estimates of functional constraint are superior to more detailed estimates provided by deep mutational scanning (DMS) measurements from a single background strain.
  These results suggest that future forecasting models should strive not to replace genetic fitness metrics with phenotypic metrics but to identify metrics that are the least likely to be affected by historical contingency.
